Demonstration of matching route networks

### 2024-01-29 r/README.qmd

>>>>

For local development run this in the `r` directory:

```{r}
devtools::load_all()
```

```{r}
library(dplyr)
```

## Example

```{r}
edinburgh_zones = zonebuilder::zb_zone("Edinburgh")
edinburgh_central_3km = edinburgh_zones |>
  filter(circle_id <= 2) |>
  sf::st_union()
osm_edinburgh_central = osmextract::oe_get_network("Edinburgh", boundary = edinburgh_central_3km, boundary_type = "clipsrc")
meuse_lane = osm_edinburgh_central |>
  filter(name == "Meuse Lane")
meuse_lane_buffer = sf::st_buffer(meuse_lane, 100)
osm_edinburgh_central = osm_edinburgh_central |>
  sf::st_intersection(meuse_lane_buffer)
osm_edinburgh_central |>
  select(highway) |>
  plot()
```

```{r}
princes_street_central = osm_edinburgh_central |>
  mutate(n = 1:n()) |>
  filter(name == "Princes Street")
princes_street_central |>
  select(highway) |>
  plot()
# Check each link:
princes_street_central |>
  select(n) |>
  plot(lwd = 5)
```

```{r}
princes_street_minimal = princes_street_central |>
  slice(1:4)
princes_street_minimal = princes_street_minimal |>
  mutate(value = 1:n()) |>
  select(value, name, osm_id)
princes_street_minimal |>
  select(value) |>
  plot(lwd = 5)
```

```{r}
m = mapview::mapview(princes_street_minimal)
princes_street_minimal_x = mapedit::editMap(m)
names(princes_street_minimal_x)
princes_street_minimal_x_1 = princes_street_minimal_x$drawn
princes_street_minimal_x_1 = princes_street_minimal_x_1 |>
  transmute(id = 1:n())
```

```{r}
bind_rows(
  princes_street_minimal |>
    transmute(layer = "y"),
  princes_street_minimal_x_1 |>
    transmute(layer = "x")
) |>
  plot(lwd = 5)
```

```{r}
dir.create("data-raw")
dir.create("data-raw/geojson")
sf::write_sf(princes_street_minimal, "data-raw/geojson/princes_street_minimal.geojson")
sf::write_sf(princes_street_minimal_x_1, "data-raw/geojson/princes_street_minimal_x_1.geojson")
```

```{r}
```
